### 2011-03-25 docs/introduction/introduction.tex
update some paper references

\noindent We have two papers in preparation that describe applications of the
method:
\begin{itemize}
\item {\em The Convective Phase Preceding Type Ia Supernovae,}
  M. Zingale, A. S. Almgren, J. B. Bell, C. M. Malone, A. Nonaka, \& S. E. Woosley 2010,
  in preparation (henceforth paper V)
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2010,
  in preparation (henceforth ``the XRB paper'')
\end{itemize}

>>>>

\noindent We have two papers that describe applications of the
method to Type Ia supernovae and X-ray bursts:
\begin{itemize}
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2011,
  ApJ, 728, 118 (henceforth ``the XRB paper'')
\item {\em The Convective Phase Preceding Type Ia Supernovae,}
  M. Zingale, A. S. Almgren, J. B. Bell, C. M. Malone, A. Nonaka, \& S. E. Woosley 2011,
  submitted to ApJ (henceforth paper V)
\end{itemize}
